### 2013-11-11 src2/thesis.tex
update

Obsidian is an embedded language for general purpose programming of GPUs. We try to strike 
a balance between high level, productivity increasing abstractions and low-level 
control needed for performance. Obsidian programs are compiled into CUDA C code.

@@

EmbArBB embeds a preexisting library for data-parallelism into Haskell and we obtain 
very good performance at little implementation effort. This performance comes from the 
expertise and effort put into the ArBB system and that we get for free. Embedding ArBB is 
a way to provide these benefits to the Haskell programmer and a way to increase usefulness
of an existing system by opening it up to a wider audience. Obsidian is very different; it 
is not based on a set of high-level parallel primitives. The Obsidian programmer 
can implement these primitives in different ways and then select the best one. 
We have obtained very good performance in case studies involving reductions.

>>>>

Obsidian is an embedded language for general purpose programming of GPUs. We try to strike 
a balance between high level, productivity increasing abstractions and low-level 
control needed for performance. The Obsidian programming model mirrors the GPU arhcitecture 
and the programmer is constrained into writing GPU-friendly code. By supplying hierarchy level 
polymorphic library functions, these constraints does not feel obtrusive. Obsidian programs are 
compiled into CUDA C code. This compilation is based on a simple and elegant monad reification 
technique.

@@

EmbArBB embeds a preexisting library for data-parallelism into Haskell and we obtain 
very good performance at little implementation effort. This performance comes from the 
expertise and effort put into the ArBB system and that we get for free. Embedding ArBB is 
a way to provide these benefits to the Haskell programmer and a way to increase usefulness
of an existing system by opening it up to a wider audience. Obsidian is very different; it 
is not based on a set of high-level parallel primitives. The Obsidian programmer 
can implement these primitives in different ways and then select the best one. 
We have obtained very good performance in case studies involving reductions. Obsidian 
programs are also more terse and composable, compared to CUDA.
